---
title: "CDS Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
df_sentiment<-read.csv('googleplaystore_user_reviews.csv')
head(df_sentiment)
```

```{r}
library(ggplot2)
ggplot(data = df_sentiment,aes(x = Sentiment,fill = Sentiment))+
  geom_bar()+
  labs(title = 'Frequency Plot of Sentiment',x = 'Sentiment',y = 'Frequency' )
```
```{r}
```
We need to remove the nan values from the data.
The Number of positive in our data set is much larger compared to the number of negative and the number of neutral. This dispropotionate will result in a higher chance of predicting them to be positive. 
Accuracy might not be a good measure to evaluate the model. 
We should consider to use tree-based algorithms. Decision trees often perform well on imbalanced datasets because their hierarchical structure allows them to learn signals from both classes.


```{r}
str(df_sentiment)
summary(df_sentiment)
```
All rows from the nan should be removed. 
Classifying a sentence as subjective or objective, known as subjectivity classification.
Classifying a sentence as expressing a positive, negative or neutral opinion, known as polarity classification.

Thus, we can consider to add a column to the existing dataframe in which  Sentimnet_Subjectivity>0.5 will be classfied as subjective, else objective 
```{r}
df_sentiment = transform(df_sentiment,Opinion = ifelse(Sentiment_Subjectivity>0.5,'Subjective','Objective'))
head(df_sentiment)
```
```{r}
library(ggplot2)
ggplot(data = df_sentiment,aes(x = Opinion,fill = Opinion))+
  geom_bar()+
  labs(title = 'Frequency Plot of Opinion',x = 'Opinion',y = 'Frequency' )
```
The visualization for the relationship between sentiment_polarity and sentiment_subjectivity was not useful 

```{r}
ggplot(data = df_sentiment,aes(x = Sentiment_Polarity,y = Sentiment_Subjectivity))+ geom_point()
```
The raltionship between sentiment polarity and sentiment can be better represent by using a boxplot as shown below
```{r}
ggplot(data = df_sentiment,aes(x = Sentiment,y = Sentiment_Polarity))+ geom_point()
```
```{r}
#Jitter plot will shift the overlap points a bit which enables us to see the actual number of points 
ggplot(data = df_sentiment,aes(x = Sentiment,y = Sentiment_Polarity))+ geom_jitter()
```


```{r}
ggplot(data = df_sentiment,aes(x = Sentiment, y = Sentiment_Polarity, fill = Sentiment))+geom_boxplot()
```

```{r}
ggplot(data = df_sentiment,aes(x = Sentiment, y = Sentiment_Subjectivity, fill = Sentiment))+geom_boxplot()

```

```{r}

ggplot(data = df_sentiment,aes(x = Opinion, y = Sentiment_Subjectivity, fill = Opinion))+geom_boxplot()

```

```{r}
ggplot(data = df_sentiment,aes(x = Opinion, y = Sentiment_Polarity, fill = Opinion))+geom_boxplot()
```
```{r}
library(ggplot2)
ggplot(data = df_sentiment,aes(x = Sentiment_Polarity))+
  geom_histogram()+
  labs(title ='Histogram of Sentiment Polarity',x = 'Sentiment Polarity',y = 'Frequency' )

```
```{r}
library(ggplot2)
ggplot(data = df_sentiment,aes(x = Sentiment_Subjectivity))+
  geom_histogram()+
  labs(title ='Histogram of Sentiment Subjectivity ',x = 'Sentiment Subjectivity',y = 'Frequency' )


```

Additional plots that can be considered: 
Boxplots with both the sentiment subjectivity and sentiment polarity 

The following plots required us to tokenize the review and get the word count before we can proceed. 

Plots required:
Word count,
Most Frequent word in the positive sentiment,
Most Freqeunt word in the negative sentiment,
Most Frequesnt word in the neutral sentiment,
Method : Can use word cloud, bar chart 




